%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REV403: Thu 23 Feb 2023 07:00
% REV382: Thu 30 Jun 2022 15:00
% REV328: Sat 14 Aug 2021 06:00
% REV316: Wed 14 Jul 2021 13:00
% REV182: Wed Jan 23 2020 12:00
% STARTX: Thu Aug 16 2020 22:00
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{TIPS}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{TIPS (1)}

\begin{itemize}

\item See also \url{https://rms46.vlsm.org/2/221.pdf}.

\item Register yourself via Google Forms as soon as possible. 
      No need to wait until your SIAK is approved (RMS)!

\item For any administrative issues, contact SEKRE at building B, $2^{nd}$ floor --
      especially for absences, illness, sick letters, follow-up exams, etc.
      Please do not contact the \textbf{Lecturer} (RMS).

\item Please complete the follow-up/paper work within six (6) working days (RMS).

\end{itemize}

\end{frame}

% (10) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[fragile]
\frametitle{TIPS (2)}

\begin{itemize}

\item Study the Operating System Concept book, which deals with the material that
      will be discussed that week (MIM). Make a summary of the material in your Memo (IP).

\item You should understand every single problem of the past examinations.
      Write down all hints in your ''\textbf{MEMO}'' (MHP).

\item You are allowed to bring a sheet of MEMO for the midterm (UTS) and
     a sheet for the finalterm (UAS) (RMS).

\item You should understand every single line of the ''\textbf{DEMOS}'' (MHP).

\item You should ask \textbf{the lecturer} or anyone, anything you do not understand (TA).

\item The \textbf{ASDOS} are the lectures's helper, not your personal tutors (RMS).

\end{itemize}

\end{frame}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]
\frametitle{Special Thanks}

\begin{tabular}{|p{117mm}|}
\hline
\vspace{1mm}

\textbf{Special thanks} for writing and reviewing this material to: \\ [2mm]

\begin{tabular}{p{109mm}}
Anisha Inas Izdihar (AII),
Benedictus Alvin (BA),
Dennis Al Baihaqi Walangadi,
Dionisius Baskoro Samudra,
Eugene Brigita Lauw,
Ibnu Sofian Firdaus (ISF),
Irmanpen Panjaitan (IP),
Ivana Irene Thomas (IIT),
Marcia Nadin Pramasiwi,
Michael Giorgio Wirawan (MGW),
Muhamad Yoga Mahendra,
Muhammad Afkar (MA),
Muhammad Hanif Pratama (MHP),
Muhammad Iqbal Mahendra (MIM),
Muhammad Krishertanto Adityapu,
M. Ikhsan Kurniawan (MIK),
Nixi Sendya Putri (NSP),
Raihan Mahendra Sutanto (RM),
Rizki Leonardo (RL),
Shavira Adeva (SA),
Stefan Mayer Sianturi (SMS),
Thrisnadevany Amalia (TA),
Zhelia Alifa (ZA); \\ [2mm]
\end{tabular}
\\ [3mm]
\hline
\end{tabular}

\end{frame}

