%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REV412: Tue 22 Aug 2023 16:00
% REV410: Wed 09 Aug 2023 08:30
% REV409: Tue 08 Aug 2023 12:00
% REV406: Sat 05 Aug 2023 12:00
% REV154: Thu 23 Aug 2018 11:00
% START0: Thu 26 Jul 2018 20:00
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Week 00}
\begin{frame}[fragile]
\frametitle{Week 00 Overview I:
Topics\footnote{Source: ACM IEEE CS Curricula}}

\begin{itemize}
\item Role and purpose of the operating system 
\item Functionality of a typical operating system 
\item Mechanisms to support client-server models, hand-held devices 
\item Design issues (efficiency, robustness, flexibility, portability, security, compatibility) 
\item Influences of security, networking, multimedia, windowing systems 
\item Structuring methods (monolithic, layered, modular, micro-kernel models) 
\item Abstractions, processes, and resources 
\item Concepts of application program interfaces (APIs) 
\item The evolution of hardware/software techniques and application needs 
\item Device organization 
\item Interrupts: methods and implementations 
\item Concept of user/system state and protection, transition to kernel mode 
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Week 00 Overview I:
Learning Outcomes (1)\footnote{Source: ACM IEEE CS Curricula}}
\begin{itemize}
\item Explain the objectives and functions of modern operating systems [Familiarity]
\item Analyze the tradeoffs inherent in operating system design [Usage]
\item Describe the functions of a contemporary operating system with respect to convenience, efficiency, and the ability to evolve. [Familiarity] 
\item Discuss networked, client-server, distributed operating systems and how they differ from single user operating systems. [Familiarity] 
\item Identify potential threats to operating systems and the security features design to guard against them. [Familiarity] 
\item Explain the concept of a logical layer.  [Familiarity] 
\end{itemize}
\end{frame}


\begin{frame}[fragile]
\frametitle{Week 00 Overview I:
Learning Outcomes (2)\footnote{Source: ACM IEEE CS Curricula}}
\begin{itemize}
\item Explain the benefits of building abstract layers in hierarchical fashion.  [Familiarity] 
\item Describe the value of APIs and middleware. [Assessment]
\item Describe how computing resources are used by application software and managed by system software.  [Familiarity] 
\item Contrast kernel and user mode in an operating system. [Usage]
\item Discuss the advantages and disadvantages of using interrupt processing. [Familiarity] 
\item Explain the use of a device list and driver I/O queue. [Familiarity] 
\end{itemize}
\end{frame}

