%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REV340 Sun 05 Sep 2021 17:25:57 WIB
% REV330 Wed 18 Aug 2021 11:05:51 WIB
% REV161 Thu Sep  6 09:24:27 WIB 2018
% REV154 Thu Aug 23 11:22:02 WIB 2018
% START0 Thu Jul 26 20:01:45 WIB 2018
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Week 01}
\begin{frame}[fragile]
\frametitle{Week 01 Overview II:
Topics\footnote{Source: ACM IEEE CS Curricula 2013}}

\begin{itemize}
\item Intelectual Property Rights (IPR)
\item Software Licenses and Free Software
\item Operating System Services and Interfaces
\item System Calls and System Programming
\item Types of virtualization (including Hardware/Software, OS, Server, Service, Network) 
\item Hypervisors 
\item Portable and cost of virtualization; emulation vs. isolation 
\item Cloud services: IAAS, PAAS and Platform APIs, SAAS
\item Introduction to Scripting and REGEX.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Week 01 Overview II:
Learning Outcomes\footnote{Source: ACM IEEE CS Curricula 2013}}

\begin{itemize}
\item Explain the concept of virtual memory and how it is realized in hardware and software. [Familiarity] 
\item Discuss hypervisors and the need for them in conjunction with different types of hypervisors. [Usage] 
\item Differentiate emulation and isolation. [Familiarity]
\item Evaluate virtualization trade-offs. [Assessment]
\item Discuss the importance of elasticity and resource management in cloud computing. [Familiarity]
\item Explain the advantages and disadvantages of using the virtualized infrastructure. [Familiarity]
\end{itemize}
\end{frame}

